---
title: "BSMM-lab-5"
subtitle: "BSMM 8740 Fall 2023"
author: "Add your name here"
date: "Add the date here"
format: html
editor: visual
self-contained: true
---

::: callout-note
## REMINDER:

Be sure to edit this document (see above) to include your name (and the date)

Before you wrap up the assignment, make sure all documents are updated on your GitHub repo (i.e. save, stage, commit and push).

Remember -- you do **not** have to turn in an \*.html file. I will be pulling your work directly from your repository on the [course github site](https://github.com/BSMM-8740-Fall-2023).
:::

## Setup

Today we will be using the Ames Housing Data.

This is a data set from [De Cock](http://jse.amstat.org/v19n3/decock.pdf) (2011) has 82 fields were recorded for 2,930 properties in Ames Iowa in the US. The version in the `modeldata` package is copied from the `AmesHousing` package but does not include a few quality columns that appear to be outcomes rather than predictors.

```{r}
#| eval: false
dat <- modeldata::ames
```

The data dictionary can be found on the internet:

```{r}
#| eval: false
cat(readr::read_file("http://jse.amstat.org/v19n3/decock/DataDocumentation.txt"))
```

## Exercises

### Exercise 1

Write and execute the code to perform summary EDA on the Ames Housing data using the package `skimr`. Show the results.

### Exercise 2

Write and execute code to create training and test datasets. Have the training dataset represent 75% of the total data. Name the training dataset **ames_train** and the test dataset **ames_test**

### Exercise 3

Create a recipe based on the formula **Sale_Price \~ Longitude + Latitude + Lot_Area + Neighborhood + Year_Sold** and with the pre-processing steps specified in the description. Show the output of `broom::tidy()` with your recipes as the argument.

### Exercise 4

Create three regression models using the `parsnip::` package and assign each model to its own variable

-   a base regression model using `lm`
-   a regression model using `glmnet`; set the model parameters `penalty` and `mixture` for tuning
-   a tree model using the `ranger` engine; set the model parameters `min_n` and `trees` for tuning

Evaluate (print) each model variable to show the type of model, the method of fitting and the tuning arguments, if any.

### Exercise 5

Use `parsnip::translate()` on each model to see the model template for each method of fitting.

### Exercise 6

Create bootstrap samples for the training dataset. You can leave the parameters set to their defaults.

### Exercise 7

Create workflows with `workflowsets::workflow_set` using your recipe and models. Show the resulting datastructure, noting the number of columns, and then use `tidyr::` to unnest the *info* column and show its contents.

### Exercise 8

Use `workflowsets::workflow_map` to map the default function (`tune::tune_grid()` - look at the help for `workflowsets::workflow_map` ) across the workflows in the workflowset you just created and update the variable `all_workflows` with the result.

The updated variable `all_workflows` contains a nested column named **result**, and each cell of the column **result** is a tibble containing a nested column named **.metrics**. Write code to

1.  un-nest the metrics in the column .metrics
2.  filter out the rows for the metric rsq
3.  group by wflow_id, order the .estimate column from highest to lowest, and pick out the first row of each group.

### Exercise 9

Run the code provided and compare to your results from exercise 8.

### Exercise 10

Select the best model per the **rsq** metric using its id.

What is the ratio of the OOB prediction errors (MSE): test/train?
